### 2021-07-30 doc/thesis/chapters/results.tex
bit smaller figure
Fig. -> Figure
sysdesign

\subsubsection{Comparing against the Matlab reference}

In the comparison against the Matlab model, the HLS variant achieves a very exact match of the output signal.
However, the VHDL implementation differs by a certain amount.
There seems to be an issue in the signal separation between the left and right audio channels.
This is visible in the analysis of the audio signal, as shown is Fig. \ref{fig:audio_output_compare_tb_vs_hw}.
The signal strength of the left channel in the upper diagram is weaker than expected, while the right channel in the lower diagram is stronger.
This imbalance can also be observed by listening to the audio output via speakers.\\

@@

\subsubsection{Comparing simulation- against hardware results}

@@

Again, the time limitation in the elaboration of this thesis does not allow a deeper analysis of this issue.
However, the end-to-end system design enables the developer to analyze an issue like this in a convenient way, in quick iterations.
Any adaptions in the VHDL design can be simulated and integrated into the FPGA with automated scripts.
Both results can then be analyzed and compared, which may lead to further adaptions.\\

@@

%%%%%%%%%%%%%%%%%%%%
\subsection{Lines of Code}
% of the entire project

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Simulation}
% Sim speed of x min of recorded FM signal

@@

% - The system level architecture that was chosen, can be applied to any DSP project. Simply replace the main IP, e.g. from FM to DAB+, QAM, etc. and the environment can run in the exact same way.

>>>>

%%%%%
\subsubsection{Comparing against the Matlab reference}

In the comparison against the Matlab model, the HLS variant achieves a very exact match of the output signal.
However, the VHDL implementation differs by a certain amount.
There seems to be an issue in the signal separation between the left and right audio channels.
This is visible in the analysis of the audio signal, as shown is Figure \ref{fig:audio_output_compare_tb_vs_hw}.
The signal strength of the left channel in the upper diagram is weaker than expected, while the right channel in the lower diagram is stronger.
This imbalance can also be observed by listening to the audio output via speakers.\\

@@

%%%%%
\subsubsection{Comparing simulation- against hardware results}

@@

Again, the time limitation in the elaboration of this thesis does not allow a deeper analysis and investigation of this issue.
However, the end-to-end system design enables the developer to analyze an issue like this in a convenient way, in quick iterations.
Any adaptions in the VHDL design can be simulated and integrated into the FPGA with automated scripts.
Both results can then be analyzed and compared, which may lead to further adaptions.\\

@@

asdf

%%%%%%%%%%%%%%%%%%%%
\subsection{Lines of Code}

% of the entire project
asdf

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Simulation}
% Sim speed of x min of recorded FM signal
%
% VHDL:
%          time                samples
%   audio         sim        in      out
%  0.1000 s    73:44 min  (96000 -> 4000)
%  0.0100 s    09:37 min  ( 9600 ->  400)
%  0.0025 s    02:36 min  ( 2400 ->  100)
%
% HLS:

@@

The system design architecture that is chosen in this project covers several parts of the system.
This includes a reference model, the development of the IP itself, including the simulation testbench, as well as the final integration into the productive system.
Because of this structured approach, that is given by this system design, it can be applied to almost any DSP project.
The main processing IP can simply be replaced with another implementation, while the environment does not need to be modified.
The reason therefor is, that DSP projects almost always use streaming interfaces for their inputs and outputs.
Also a configuration interface is commonly used, to adapt certain parameters of the IP during runtime.
